---
title: "CADU-SINASC Descriptive Anlaysis Visualizations"
author: Ryan Hafen
output:
  rmdformats::html_clean:
    fig_width: 8
    fig_height: 6
    highlight: kate
    thumbnails: false
    lightbox: false
    gallery: false
    self_contained: false
---


<link rel="stylesheet" href="lib/magnific-popup.css">
<script src="lib/jquery.magnific-popup.js"></script>

<style>
  .popup-gallery {
    width: 800px
  }
  .item {
    position: relative;
    padding: 0px;
    display: inline-block;
  }
  .item img {
    margin: 0px;
    padding: 0px;
  }
  .item-label {
    position: absolute;
    top: 0;
    width: 150px;
    text-align: center;
    background: black;
    opacity: 0.6;
    color: white;
  }
  .mfp-title {
    color: darkgray !important;
    padding-left: 10px !important;
  }
  .mfp-counter {
    color: darkgray !important;
    padding-right: 10px !important;
  }
</style>

<script>
$(document).ready(function() {
	$('.popup-gallery').magnificPopup({
		delegate: 'a',
		type: 'image',
		tLoading: 'Loading plot #%curr%...',
		mainClass: 'mfp-img-mobile',
		gallery: {
			enabled: true,
			navigateByImgClick: true,
			preload: [0,1] // Will preload 0 - before current, and 1 after the current image
		},
		image: {
			tError: '<a href="%url%">The plot #%curr%</a> could not be loaded.',
			titleSrc: function(item) {
				return item.el.attr('title');
			}
		}
	});
});
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

plot_gallery <- function(path) {
  f <- list.files(path, full.names = TRUE,
    pattern = ".png")
  f2 <- gsub("plots/", "plots/_thumbs/", f)

  library(png)
  img <- readPNG(f[1])

  dm <- dim(img)
  width <- 150
  height <- width * dm[1] / dm[2]

  nm <- basename(f)
  nm <- gsub("\\.png", "", nm)

  aa <- paste0("<div class='item'><a href='", f, "' title='", basename(path), "/", nm, ".png'><img src='",
    f2, "' width='", width, "', height='", height, "'><div class='item-label'>", nm, "</div></a></div>")

  cat(paste0("<div class='popup-gallery'>",
    paste(aa, collapse = ""), "</div>"))
}
```

## Overview

This document provides several plots of descriptive statistics of outcomes of interest vs. various risk factors in the CADU-SINASC linked dataset. Unless otherwise noted, the plots display point estimates of means or proportions, with 95% confidence intervals for those estimates.

Please make note of the y-axis limits when looking at the plots. The range of the axis is not consistent across plots, so some effects may appear larger than others. In cases where the point estimates don't vary too much between groups within the same plot, extra padding has been added to the axis to help with this.

Every thumbnail image below can be clicked on for closer viewing.

## Birth weight z-score

```{r echo=FALSE, results="asis"}
plot_gallery("plots/brthwt_z_summ")
```

## LBW

```{r echo=FALSE, results="asis"}
plot_gallery("plots/brthwt_cat_summ")
```

## SGA

```{r echo=FALSE, results="asis"}
plot_gallery("plots/sga_summ")
```

## SGA by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/sga_rf_geo_summ")
```

## LGA

```{r echo=FALSE, results="asis"}
plot_gallery("plots/lga_summ")
```

## LGA by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/lga_rf_geo_summ")
```

## GA at birth

```{r echo=FALSE, results="asis"}
plot_gallery("plots/gest_weeks_summ")
```

## GA at birth by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/preterm_rf_geo_summ")
```

## Cesarean

```{r echo=FALSE, results="asis"}
plot_gallery("plots/deliv_type_summ")
```

## Cesarean by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/cesarean_rf_geo_summ")
```

## Variable distribution by year and state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/geo_time_summ")
```
