---
title: "CADU-SINASC Descriptive Anlaysis Visualizations"
author: Ryan Hafen
output:
  rmdformats::html_clean:
    fig_width: 8
    fig_height: 6
    highlight: kate
    thumbnails: false
    lightbox: false
    gallery: false
    self_contained: false
---


<link rel="stylesheet" href="lib/magnific-popup.css">
<script src="lib/jquery.magnific-popup.js"></script>

<style>
  .popup-gallery {
    width: 800px
  }
  .item {
    position: relative;
    padding: 0px;
    display: inline-block;
  }
  .item img {
    margin: 0px;
    padding: 0px;
  }
  .item-label {
    position: absolute;
    top: 0;
    width: 150px;
    text-align: center;
    background: black;
    opacity: 0.6;
    color: white;
  }
  .mfp-title {
    color: darkgray !important;
    padding-left: 10px !important;
  }
  .mfp-counter {
    color: darkgray !important;
    padding-right: 10px !important;
  }
</style>

<script>
$(document).ready(function() {
	$('.popup-gallery').magnificPopup({
		delegate: 'a',
		type: 'image',
		tLoading: 'Loading plot #%curr%...',
		mainClass: 'mfp-img-mobile',
		gallery: {
			enabled: true,
			navigateByImgClick: true,
			preload: [0,1] // Will preload 0 - before current, and 1 after the current image
		},
		image: {
			tError: '<a href="%url%">The plot #%curr%</a> could not be loaded.',
			titleSrc: function(item) {
				return item.el.attr('title');
			}
		}
	});
});
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

plot_gallery <- function(path) {
  f <- list.files(path, full.names = TRUE,
    pattern = ".png")
  f2 <- gsub("plots/", "plots/_thumbs/", f)

  library(png)
  img <- readPNG(f[1])

  dm <- dim(img)
  width <- 150
  height <- width * dm[1] / dm[2]

  nm <- basename(f)
  nm <- gsub("\\.png", "", nm)

  aa <- paste0("<div class='item'><a href='", f, "' title='", basename(path), "/", nm, ".png'><img src='",
    f2, "' width='", width, "', height='", height, "'><div class='item-label'>", nm, "</div></a></div>")

  cat(paste0("<div class='popup-gallery'>",
    paste(aa, collapse = ""), "</div>"))
}

summm <- structure(list(major_degree = structure(c(1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA), .Label = c("false", "true"
), class = "factor"), deliv_type = structure(c(1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, NA, NA, NA, NA, NA, NA, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, NA, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, NA), .Label = c("Normal", 
"Cesarean"), class = "factor"), preterm = structure(c(1L, 1L, 
2L, 2L, 3L, 3L, 4L, 4L, 5L, 5L, 6L, 6L, 7L, 7L, 8L, 8L, 9L, 9L, 
NA, NA, 1L, 1L, 2L, 2L, 3L, 3L, 4L, 4L, 5L, 5L, 6L, 6L, 7L, 7L, 
8L, 8L, 9L, 9L, NA, NA, 5L, 5L, 6L, 6L, NA, NA, 1L, 1L, 2L, 2L, 
3L, 3L, 4L, 4L, 5L, 5L, 6L, 6L, 7L, 7L, 8L, 8L, 9L, 9L, NA, NA, 
1L, 1L, 2L, 2L, 3L, 3L, 4L, 4L, 5L, 5L, 6L, 6L, 7L, 7L, 8L, 8L, 
9L, 9L, NA, NA, 5L, 1L, 1L, 2L, 2L, 3L, 3L, 4L, 4L, 5L, 5L, 6L, 
6L, 7L, 7L, 8L, 8L, 9L, 9L, NA, NA, 1L, 2L, 2L, 3L, 3L, 4L, 4L, 
5L, 5L, 6L, 6L, 7L, 7L, 8L, 8L, 9L, NA, NA, NA), .Label = c("Extremely Preterm", 
"Very Preterm", "Premature", "Late Premature", "Early Term", 
"Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    birth_year = c(2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 
    2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 2014L, 2013L, 
    2013L, 2014L, 2013L), n = c(469L, 397L, 518L, 440L, 816L, 
    770L, 5234L, 4934L, 19325L, 19500L, 37818L, 39906L, 5315L, 
    5045L, 1038L, 772L, 392L, 243L, 164L, 113L, 234L, 255L, 657L, 
    615L, 862L, 832L, 4760L, 4437L, 22210L, 21353L, 28241L, 28931L, 
    4265L, 4124L, 891L, 710L, 307L, 218L, 106L, 119L, 4L, 2L, 
    4L, 5L, 1L, 1L, 42L, 41L, 43L, 33L, 50L, 56L, 409L, 465L, 
    1942L, 2284L, 2818L, 3434L, 300L, 393L, 51L, 46L, 13L, 15L, 
    9L, 11L, 69L, 86L, 191L, 176L, 285L, 254L, 2101L, 2206L, 
    15088L, 15238L, 10320L, 11469L, 548L, 566L, 100L, 117L, 26L, 
    37L, 40L, 36L, 2L, 1L, 3L, 1L, 1L, 2L, 1L, 10L, 10L, 22L, 
    43L, 55L, 75L, 8L, 22L, 2L, 2L, 1L, 1L, 30L, 10L, 1L, 1L, 
    1L, 4L, 2L, 6L, 10L, 40L, 53L, 51L, 49L, 7L, 6L, 1L, 2L, 
    1L, 38L, 3L, 1L)), row.names = c(NA, -126L), class = c("grouped_df", 
"tbl_df", "tbl", "data.frame"), vars = c("major_degree", "deliv_type", 
"preterm"), drop = TRUE)

sp_summ1 <- list(`No Major Degree` = structure(list(preterm = structure(1:9, .Label = c("Extremely Preterm", 
"Very Preterm", "Premature", "Late Premature", "Early Term", 
"Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(866L, 958L, 1586L, 10168L, 38825L, 77724L, 10360L, 
    1810L, 635L), Cesarean = c(489L, 1272L, 1694L, 9197L, 43563L, 
    57172L, 8389L, 1601L, 525L), `Total Births` = c(1355L, 2230L, 
    3280L, 19365L, 82388L, 134896L, 18749L, 3411L, 1160L), `Percent Cesarean` = c(36.1, 
    57, 51.6, 47.5, 52.9, 42.4, 44.7, 46.9, 45.3)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)), `Major Degree` = structure(list(
    preterm = structure(1:9, .Label = c("Extremely Preterm", 
    "Very Preterm", "Premature", "Late Premature", "Early Term", 
    "Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(83L, 76L, 106L, 874L, 4226L, 6252L, 693L, 97L, 
    28L), Cesarean = c(155L, 367L, 539L, 4307L, 30326L, 21789L, 
    1114L, 217L, 63L), `Total Births` = c(238L, 443L, 645L, 5181L, 
    34552L, 28041L, 1807L, 314L, 91L), `Percent Cesarean` = c(65.1, 
    82.8, 83.6, 83.1, 87.8, 77.7, 61.6, 69.1, 69.2)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)))

sp_summ2 <- list(`No schooling` = structure(list(preterm = structure(1:9, .Label = c("Extremely Preterm", 
"Very Preterm", "Premature", "Late Premature", "Early Term", 
"Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(2L, 1L, 4L, 30L, 72L, 154L, 20L, 3L, 1L), Cesarean = c(2L, 
    1L, 6L, 19L, 52L, 83L, 9L, 4L, 2L), `Total Births` = c(4L, 
    2L, 10L, 49L, 124L, 237L, 29L, 7L, 3L), `Percent Cesarean` = c(50, 
    50, 60, 38.8, 41.9, 35, 31, 57.1, 66.7)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)), `Fundamental Education I (1ª a 4ª série)` = structure(list(
    preterm = structure(1:9, .Label = c("Extremely Preterm", 
    "Very Preterm", "Premature", "Late Premature", "Early Term", 
    "Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(23L, 36L, 64L, 340L, 1260L, 2671L, 376L, 78L, 
    24L), Cesarean = c(12L, 42L, 41L, 251L, 868L, 1409L, 245L, 
    49L, 17L), `Total Births` = c(35L, 78L, 105L, 591L, 2128L, 
    4080L, 621L, 127L, 41L), `Percent Cesarean` = c(34.3, 53.8, 
    39, 42.5, 40.8, 34.5, 39.5, 38.6, 41.5)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)), `Fundamental Education II (5ª a 8ª série)` = structure(list(
    preterm = structure(1:9, .Label = c("Extremely Preterm", 
    "Very Preterm", "Premature", "Late Premature", "Early Term", 
    "Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(233L, 319L, 510L, 3042L, 10827L, 21560L, 2904L, 
    568L, 216L), Cesarean = c(99L, 274L, 363L, 1632L, 5821L, 
    9971L, 1814L, 348L, 123L), `Total Births` = c(332L, 593L, 
    873L, 4674L, 16648L, 31531L, 4718L, 916L, 339L), `Percent Cesarean` = c(29.8, 
    46.2, 41.6, 34.9, 35, 31.6, 38.4, 38, 36.3)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)), `Middle Education (antigo 2º Grau)` = structure(list(
    preterm = structure(1:9, .Label = c("Extremely Preterm", 
    "Very Preterm", "Premature", "Late Premature", "Early Term", 
    "Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(572L, 561L, 939L, 6325L, 24972L, 50377L, 6683L, 
    1109L, 367L), Cesarean = c(327L, 828L, 1124L, 6352L, 30739L, 
    40437L, 5820L, 1091L, 355L), `Total Births` = c(899L, 1389L, 
    2063L, 12677L, 55711L, 90814L, 12503L, 2200L, 722L), `Percent Cesarean` = c(36.4, 
    59.6, 54.5, 50.1, 55.2, 44.5, 46.5, 49.6, 49.2)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)), `Higher Education Incomplete` = structure(list(
    preterm = structure(1:9, .Label = c("Extremely Preterm", 
    "Very Preterm", "Premature", "Late Premature", "Early Term", 
    "Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(36L, 41L, 69L, 431L, 1694L, 2962L, 377L, 52L, 
    27L), Cesarean = c(49L, 127L, 160L, 943L, 6083L, 5272L, 501L, 
    109L, 28L), `Total Births` = c(85L, 168L, 229L, 1374L, 7777L, 
    8234L, 878L, 161L, 55L), `Percent Cesarean` = c(57.6, 75.6, 
    69.9, 68.6, 78.2, 64, 57.1, 67.7, 50.9)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)), `Higher Education` = structure(list(
    preterm = structure(1:9, .Label = c("Extremely Preterm", 
    "Very Preterm", "Premature", "Late Premature", "Early Term", 
    "Term", "Late Term", "42 Weeks", "43 or 44 Weeks"), class = "factor"), 
    Normal = c(83L, 76L, 106L, 874L, 4226L, 6252L, 693L, 97L, 
    28L), Cesarean = c(155L, 367L, 539L, 4307L, 30326L, 21789L, 
    1114L, 217L, 63L), `Total Births` = c(238L, 443L, 645L, 5181L, 
    34552L, 28041L, 1807L, 314L, 91L), `Percent Cesarean` = c(65.1, 
    82.8, 83.6, 83.1, 87.8, 77.7, 61.6, 69.1, 69.2)), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -9L)))
```

## Overview

This document provides several plots of descriptive statistics of outcomes of interest vs. various risk factors in the CADU-SINASC linked dataset. Unless otherwise noted, the plots display point estimates of means or proportions, with 95% confidence intervals for those estimates.

## Birth weight z-score

```{r echo=FALSE, results="asis"}
plot_gallery("plots/brthwt_z_summ")
```

## LBW

```{r echo=FALSE, results="asis"}
plot_gallery("plots/brthwt_cat_summ")
```

## SGA

```{r echo=FALSE, results="asis"}
plot_gallery("plots/sga_summ")
```

## SGA by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/sga_rf_geo_summ")
```

## LGA

```{r echo=FALSE, results="asis"}
plot_gallery("plots/lga_summ")
```

## LGA by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/lga_rf_geo_summ")
```

## GA at birth

```{r echo=FALSE, results="asis"}
plot_gallery("plots/gest_weeks_summ")
```

## GA at birth by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/preterm_rf_geo_summ")
```

## Cesarean

```{r echo=FALSE, results="asis"}
plot_gallery("plots/deliv_type_summ")
```

## Cesarean by state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/cesarean_rf_geo_summ")
```

## Variable distribution by year and state

```{r echo=FALSE, results="asis"}
plot_gallery("plots/geo_time_summ")
```
